---
title: "FARS Overview"
author: "Alice MacQueen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(farsr)
```

This package takes data compiled by the Fatality Analysis Reporting System and 
outputs graphs and tables of this data.

## Example Output Figures for FARS Data

You are able to map fatalities for a particular year and state by specifying 
a state number and year in `fars_map_state`.

```{r, fig.show='hold'}
setwd("..")
fars_map_state(state.num = 10, year = 2014)
fars_map_state(state.num = 11, year = 2014)
```

## Example Summary Table for FARS Data

You can also output a summary table of monthly fatalities for each year of FARS 
data. The following will output a table for the year 2014:

```{r, echo=FALSE, results='asis'}
knitr::kable(fars_summarize_years(years = 2014))
```


